NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-04-16 Manuscript/manuscriptPS.tex
Named the two CKP models following the naming scheme of Piggot.

   CKP-TMA$^+$ refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids)
   and CKP-Lys refers to the version with more Gromos compatible version

@@

    POPS/Na$^+$  & GROMOS-CKP-TMA$^+$ \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp1POPS303K} \\
    POPS/Na$^+$  & GROMOS-CKP-Lys \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp2POPS303K} \\

@@

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers without additional ions}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for most computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with  
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?
    A: YES. Renamed CKPs to clarify this.} \\
\end{figure}

>>>>

   CKPM refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids;
   'M' stands for Mukhopadhyay after the first published Berger-based PS simulation that used these charges)
   and CKP refers to the version with more Gromos compatible version

@@

    POPS/Na$^+$  & GROMOS-CKPM \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp1POPS303K} \\
    POPS/Na$^+$  & GROMOS-CKP \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp2POPS303K} \\

@@

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers without additional ions}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$.
    Experimental data from \cite{browning80} contain 0.1~M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for most computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
\end{figure}
